---
title: "P8105_HW5_yz4181"
author: "Yuanyuan Zeng(yz4181)"
date: "11/16/2021"
output: github_document
---
```{r stepup, echo=FALSE}
library(tidyverse)
```

## Problem 1

```{r}
## load the data set
homicide_df= read_csv("./homicide-data.csv", na = c("", "unknown")) %>% print()
```
* Description of raw dataset: The original data contains 52179 rows and 12 columns. The variables includes the case number, reported date, names and identities of victims, city and states of the cases, locations, and disposition. There are missing value in latitude and longitude columns. The value in age column is not consistent.


#### Unsolved and total homocides within each city
```{r}
## Clean data set
homicide_df = homicide_df %>% 
  mutate(city_state = str_c(city, state),
         resolution = case_when(
           disposition == "Closed without arrest" ~ "unsolved",
           disposition == "Open/No arrest" ~ "unsolved",
           disposition == "Closed by arrest" ~ "solved")) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")

# summarize within city
total_homocide = homicide_df %>% 
  select(city_state) %>% 
  group_by(city_state) %>% 
  summarize(
    total_homocides = n()) 
 
number_unsolved = homicide_df %>% 
  select(city_state, resolution) %>% 
  filter(resolution == "unsolved") %>% 
  group_by(city_state) %>% 
  summarize(
    number_unsolved = n())

summary_within_city = left_join(number_unsolved, total_homocide) %>%  print()
```
* Summary: The table showing the number of unsolved homicides and total number of homicides in each city.


#### Look at the homicides in the city of Baltimore, MD
```{r}
baltimoreMD = homicide_df %>% 
  filter(city_state == "BaltimoreMD") %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    total_homocide = n())

baltimore_test = prop.test(
  x = baltimoreMD %>% pull(unsolved),
  n = baltimoreMD %>% pull(total_homocide))

baltimore_test %>% 
  broom::tidy() %>% 
  select(
    estimate,
    conf.low,
    conf.high)
```
* The table shows that the estimate proportion of unsolved homicides in Baltimore is 0.6456 and the confident interval is between 0.6276 and 0.6632.


#### Run the prop test for each cities
```{r}
## set up function
prop_test_function = function(city_df){
  
  city_summary =
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      total = n()
      )
      
  city_test = prop.test(
    x = city_summary %>% pull(unsolved),
    n = city_summary %>% pull(total))
  
  return(city_test)
  }

## Perform prop test using map function
result_df = homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_result = map(data, prop_test_function),
    tidy_result = map(test_result, broom::tidy)
  ) %>% 
  select(
    city_state,
    tidy_result) %>% 
  unnest(tidy_result) %>% 
  select(
    city_state,
    estimate,
    starts_with("conf")) %>% 
  print()
  
## (Alternative) perform prop test using map2 function
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    total = n()) %>% 
  mutate(
    test_result = map2(unsolved, total, prop.test),
    tidy_result = map(test_result, broom::tidy)) %>% 
  unnest(tidy_result) %>% 
  select(city_state, estimate, starts_with("conf"))
  
```
* Summary: The table shows the estimate proportion of unsolved homocides and confident interval within each city.


#### Creata a plot show the estimate and CI for each city
```{r}
## Creating a plot
result_df %>% 
  mutate(
    city_state = fct_reorder(city_state, estimate)
  ) %>% 
  ggplot(aes(x= city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust =0.5, hjust = 1)) +
  labs(
    x = "City_State",
    y = "Estimate"
  )
```


## Problem 2
```{r, message=FALSE}
## Create a dataframe for all participants
all_participant_df = tibble(
  file_name = list.files(path = "./data/")) %>% 
  mutate(
    path = str_c("./data/", file_name),
    data = map(path, read_csv)) %>% 
  unnest(data) %>% 
  separate(
    file_name, into = c("arm","subject_id"), sep = "_") %>% 
  mutate(
    subject_id = str_replace(subject_id, ".csv", " ")) %>% 
  select(-path) %>% 
  print()

## Create a dataframe for participants in control arm
con_df = all_participant_df %>% 
  filter(arm == "con") %>% 
  print()
```

### Making spaghetti plot
```{r}
all_participant_df %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "weekly_observation") %>% 
  ggplot(aes(x = week, y = weekly_observation, group = subject_id)) +
    geom_line(aes(color = subject_id)) +
   facet_grid(~arm) +
  theme(axis.text.x = element_text(angle = 90, vjust =0.5, hjust = 1))
```
* Comments: Comparing two arms, we notice that the observation for all patients in experience arm are increasing over eight weeks. However, the observations for patients in control arm are relatively stable over the time. 


## Problem 3
```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

fill_in_function = function(x) {
  if (is.numeric(x)) {
    x_mean = mean(x, na.rm = TRUE)
    x = replace_na(x, x_mean)
  }
  
  if(is.character(x)) {
    x = replace_na(x, "virginica")
  }
  
  return(x)
}

iris = map(iris_with_missing, fill_in_function)
```

